\section{Related Work}
\label{sec:related}

\subsection{Knowledge Distillation for Object Detection}

Knowledge distillation, introduced by \cite{hinton2015distilling}, transfers knowledge from a large teacher network to a smaller student network by matching softened output distributions. For object detection, the challenge extends beyond classification to include localization and feature learning.

Chen et al. \cite{chen2017learning} pioneered KD for detection, proposing to distill both classification and bounding box regression outputs. Subsequent work has explored various knowledge sources: FitNets \cite{romero2014fitnets} focus on intermediate feature alignment; attention transfer methods \cite{zagoruyko2016paying} use attention maps as supervision; and localization-aware distillation \cite{dai2021general} specifically targets bounding box quality.

Recent detection KD frameworks often combine multiple distillation branches, integrating feature and attention distillation for spatial consistency, while relation-based distillation captures structural information. However, these methods are typically validated on clean datasets (COCO, ImageNet), leaving behavior under adverse conditions understudied.

\subsection{Knowledge Distillation Under Domain Shift and Adverse Conditions}

The robustness of KD to domain shift has garnered increasing attention. \cite{sun2016deep} analyze feature alignment across domains, while cross-domain KD methods explore transferring knowledge between different visual domains \cite{yang2021cross, li2022cross}. Recent work has investigated source-free domain adaptation for object detection \cite{zhang2023source}, addressing scenarios where target domain data is unavailable during training.

Adverse weather conditions present a particularly challenging domain shift scenario. \cite{guo2021meets} survey the intersection of KD and image restoration, noting that degradations like fog and haze degrade both teacher and student performance. \cite{chen2023towards} provide a comprehensive survey on robust object detection under adverse weather, highlighting the gap in understanding failure mechanisms. \cite{liu2023learning} survey image restoration methods for complex weather conditions, emphasizing the need for robust visual perception systems.

Several works have addressed fog-specific object detection. \cite{li2018benchmarking} establish benchmarks for dehazing and visibility restoration. \cite{sakaridis2018semantic} provide the Foggy Cityscapes dataset demonstrating significant performance degradation under synthetic fog. \cite{valluripalli2021foggy} propose adversarial domain transfer for foggy scene understanding. \cite{li2022domain} specifically address domain adaptive detection for autonomous driving under foggy weather. While these works acknowledge that standard detectors struggle in fog, they do not analyze how knowledge transfer specifically breaks down.

\subsection{Mechanism-Oriented Analysis of Knowledge Distillation}

Beyond proposing new methods, a growing body of work seeks to understand \emph{why} KD works or fails. \cite{phuong2019functional} provide theoretical analysis of the function learned by distillation, while \cite{cho2019efficacy} examine which aspects of teacher knowledge actually transfer. \cite{stanton2021does} empirically question whether KD always works as expected, highlighting scenarios where distillation fails to improve student performance.

Recent surveys have systematized KD research. \cite{gou2021knowledge} survey various knowledge types and their transfer mechanisms. \cite{beyer2022knowledge} focus on knowledge distillation for vision transformers, reviewing architectural considerations. \cite{wang2024robust} discuss robust visual perception for intelligent transportation systems, connecting to image communication challenges.

Empirical mechanism studies often focus on the teacher-student relationship. \cite{mirzadeh2020improved} investigate the gap between teacher and student capacity, finding that imperfect teachers can still provide useful supervision. For adverse conditions, \cite{gao2023distilling} distill localization information for robust detection, though they do not isolate specific failure mechanisms.

For failure analysis, several hypotheses recur in the literature. \textbf{Distribution mismatch} posits that domain shift disrupts the teacher output distributions that KD relies upon \cite{wang2020cross, yang2021cross}. \textbf{Uncertainty amplification} suggests that teacher predictions become unreliable under degraded inputs, amplifying errors in student training \cite{kendall2017uncertainties, qiao2023uncertainty}. \textbf{Representation misalignment} proposes that feature spaces diverge across domains, impeding feature-based distillation \cite{sun2016deep, li2022cross}.

However, these mechanisms are rarely tested against each other within a unified framework. Our work fills this gap by empirically evaluating multiple hypotheses within a controlled experimental design, determining which mechanisms receive direct support from observed behavior.
